### 2015-07-04 narrative/placement.tex
some more reorganization of the text in placement

To take advantage of these architectural trends, we propose a triplet of
data placement strategies. First, we will utilize the faster layer of the
storage hierarhcies, such as DRAM, NVRAM and remote NVRAM, as the target for
the initial write from an application. To mitigate the space concerns, we
will use the techniques described in Section~\ref{sec:refactoring} to
identify and partition the segments of data with the highest utility for the
application and use case. The rest of the data will be stored on the
parallel file system, as is done today. Second, we will utilize the
migration of data supported by the existing implementation of \Sir to move the
data to an appropriate tier. We will explore how migration can be guided by
a combination of the utility function defined by the application and the
resources avialable to the storage system. Knowing the specific structural
and semantic information (including relationships between data segments)
about the data will enable migration to partition the data further to
optimize access to data for reader. 
Finally, we will explore policies that combine the knowledge of data, its
utility to users, the cost of maintaining data in long term storage and
other metrics to decide how to purge irrelevant data from the storage
system.

Thus we propose to advance the state of the art in three connected areas:
(1) Data placement,
(2) Migration,
and (3) Purging.

>>>>

We proposed to advance the state of the art in the three major parts of the
data lifecycle. First, we will explore the optimizations and techniques to
scalably manage data when it is generated by the application. Second, we
will study the management of resources and data at rest. And finally, we will
investiage how data is consumed, either by being read and processed (for
example within analytics) or by being purged from the system.

Towards this end, we will utilize the faster layer of the
storage hierarhcies, such as DRAM, NVRAM and remote NVRAM, as the target for
the initial write from an application. To mitigate the space concerns, we
will use the techniques described in Section~\ref{sec:refactoring} to
identify and partition the segments of data with the highest utility for the
application and use case. The rest of the data will be stored on the
parallel file system, as is done today. We will leverage the supported data
mirgration techniques in \Sir to determine the most appropriate location to
move the data once its in stable storage. This migration will be guided by a
combination of the utility function defined by the application and the
resources avialable to the storage system. Knowing the specific structural
and semantic information (including relationships between data segments)
about the data will enable migration to partition the data further to
optimize access to data for reader. 
We will also explore policies that combine the knowledge of data, its
utility to users, the cost of maintaining data in long term storage and
other metrics to decide how to purge irrelevant data from the storage
system.
